\documentclass[11pt,a5paper,twoside,openany]{book}
\usepackage[pass]{geometry}

\usepackage{titlesec}
\titleformat{\chapter}
  {\bfseries} 		% format
  {\null}                % label
  {0pt}             % sep
  {\Large}           % before-code

\usepackage{latexsym}
\newenvironment{checklist}{
  \begin{list}{}{}
  
}{%
  \end{list}
}

\title{\textbf{HACMan ML7 Induction Checklists}}
\author{Gregory Morris}
\date{}
\begin{document}

\maketitle
\chapter{Health and Safety}
\begin{checklist}
\item Do not use the lathe whilst alone in the space.
\item Tie back long hair and clothing.
\item Avoid wearing gloves.
\item Wear safety glasses or goggles (Most prescription glasses are not suitable on their own).
\item Ensure the belt guard is down before starting the lathe.
\item Avoid touching the chuck or work whilst spinning.
\item Avoid touching the swarf - it can be very sharp.
\end{checklist}


\chapter{Machine Care}
\begin{checklist}
\item Materials
	\begin{checklist}
	\item Metals
	\item Plastics
	\item Wood - NO
	\item If unsure - ASK
	\end{checklist}
\item Lubrication - See chart
\item Open and close oilers as appropriate - ensure they are full first
\item If using slow gears - lubricate directly
\item Avoid lubricating belt
\end{checklist}



\chapter{Using the 3-jaw chuck}
	\begin{checklist}
	\item Mounting
	\item Changing jaws
	\item Securing work
	\item When not to use
	\end{checklist}
\chapter{Facing and Turning}
	\begin{checklist}
	\item Mount work and check for security
	\item Select and mount tool, adjust height
	\item Select appropriate speed
	\item Swing work round, ensure clearance
	\item Touch tool, take facing cuts.
		\begin{checklist}
		\item Touching tool - listen for cutting
		\item Feed rate and depth of cut
		\item Locking saddle - Why, When
		\item Importance of tool height - nub on end of work?
		\end{checklist}
	\item Turning to diameter
		\begin{checklist}
		\item Touching tool
		\item Hand feeding tool
		\item Automatic feeding
		\item Dimensional accuracy
		\end{checklist}
	\item Drill
		\begin{checklist}
		\item Tailstock controls
		\item Mounting Jacobs chuck
		\item Centre Drill
		\item Drilling
			\begin{checklist}
			\item Peck drilling
			\item Stepping up with sizes for large holes
			\end{checklist}
		\item Deburring
		\end{checklist}
	\end{checklist}
\chapter {QC}
	\begin{checklist}
	\item Using measuring tools
	\item OD correct
	\item ID correct
	\item Drill depth OK
	\item Surface Finish
	\item Free of burrs?
	\end{checklist}



\end{document}
